Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-02-03 WSSSPE3/report/WSSSPE3_review.tex
1 change: didn't -> did not
No content change. Just wrap up long lines.
No content change. Just link up some short lines.
First page: non-breaking spaces for middle initials and updated author order.

\author{Daniel S. Katz$^{(1)}$,
Kyle E.\ Niemeyer$^{(2)}$,
Sou-Cheng T. Choi$^{(3)}$,
James Hetherington$^{(4)}$,
Frank~L\"{o}ffler$^{(5)}$,
Dan Gunter$^{(6)}$,
Ray Idaszak$^{(7)}$,
Steven R. Brandt$^{(5)}$,
Mark A. Miller$^{(8)}$,
Sandra Gesing$^{(9)}$,
Nick D. Jones$^{(10)}$,
Nic Weber$^{(11)}$,
Suresh Marru$^{(12)}$,
Gabrielle Allen$^{(13)}$,
Birgit~Penzenstadler$^{(14)}$,
Colin C. Venters$^{(15)}$,
Ethan Davis$^{(16)}$,
Lorraine Hwang$^{(17)}$,
Ilian~Todorov$^{(18)}$,
Abani Patra$^{(19)}$,
Miguel de Val-Borro$^{(20)}$
}

%
\thanks{{}$^{(1)}$ Computation Institute, 
University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering, 
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(3)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; sctchoi@uchicago.edu}
%
\thanks{{}$^{(4)}$ Research Software Development Group, University College London, UK; j.hetherington@ucl.ac.uk}
%
\thanks{{}$^{(5)}$ Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA; \{knarf,sbrandt\}@cct.lsu.edu}
%
\thanks{{}$^{(6)}$ Lawrence Berkeley National Laboratory, Berkeley, USA; dkgunter@lbl.gov}
%
\thanks{{}$^{(7)}$ RENCI, University of North Carolina at Chapel Hill, Chapel Hill, NC, USA; rayi@renci.org}
%
\thanks{{}$^{(8)}$ University of California, San Diego, CA, USA; mmiller@sdsc.edu}
%
\thanks{{}$^{(9)}$ Center for Research Computing, University of Notre Dame, Notre Dame, IN, USA; sandra.gesing@nd.edu}
%
\thanks{{}$^{(10)}$ New Zealand eScience Infrastructure (NeSI), University of Auckland, Auckland, NZ; nick.jones@nesi.org.nz}
%
\thanks{{}$^{(11)}$ University of Washington, Seattle, WA, USA; nmweber@uw.edu}
%
\thanks{{}$^{(12)}$ Indiana University, Bloomington, IN, USA; smarru@iu.edu}
%
\thanks{{}$^{(13)}$ National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL, USA; gdallen@illinois.edu}
%
\thanks{{}$^{(14)}$ College of Computer Engineering \& Computer Science, California State University, Long Beach, CA, USA; birgit.penzenstadler@csulb.edu}
%
\thanks{{}$^{(15)}$ School of Computing and Engineering, University of Huddersfield, Huddersfield, UK; c.venters@hud.ac.uk}
%
\thanks{{}$^{(16)}$ UCAR Unidata, Boulder, CO, USA; edavis@ucar.edu}
%
\thanks{{}$^{(17)}$  University of California, Davis, CA, USA; ljhwang@ucdavis.edu}
%
\thanks{{}$^{(18)}$ Science \& Technology Facilities Council, UK; ilian.todorov@stfc.ac.uk}
%
\thanks{{}$^{(19)}$ Mechanical and Aerospace Engineering, University at Buffalo, Buffalo, NY, USA; abani@buffalo.edu}
%
\thanks{{}$^{(20)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA; valborro@princeton.edu}
%

@@

Progress in scientific research is dependent on the quality and accessibility of
software at all levels. Hence it is critical to address challenges related to
development, deployment, maintenance, and overall sustainability of reusable
software as well as education around software practices. These challenges can be
technological, policy based, organizational, and educational; and are of
interest to developers (the software community), users (science disciplines),
software-engineering researchers, and researchers studying the conduct of
science (science of team science, science of organizations, science of science
and innovation policy, and social science communities). The WSSSPE1 workshop
engaged a broad scientific community to identify challenges and best practices
in areas of interest to creating sustainable scientific software. WSSSPE2
invited the community to propose and discuss specific mechanisms to move towards
an imagined future for software development and usage in science and
engineering. But WSSSPE2 didn't have a good way to enact those mechanisms, or to
encourage the attendees to follow through on their intentions.

>>>>

\author{Daniel S.\ Katz$^{(1)}$,
Sou-Cheng T.\ Choi$^{(2)}$,
Kyle E.\ Niemeyer$^{(3)}$,
James Hetherington$^{(4)}$,
Frank~L\"{o}ffler$^{(5)}$,
Dan Gunter$^{(6)}$,
Ray Idaszak$^{(7)}$,
Steven R.\ Brandt$^{(5)}$,
Mark A.\ Miller$^{(8)}$,
Sandra Gesing$^{(9)}$,
Nick D.\ Jones$^{(10)}$,
Nic Weber$^{(11)}$,
Suresh Marru$^{(12)}$,
Gabrielle Allen$^{(13)}$,
Birgit~Penzenstadler$^{(14)}$,
Colin C.\ Venters$^{(15)}$,
Ethan Davis$^{(16)}$,
Lorraine Hwang$^{(17)}$,
Ilian~Todorov$^{(18)}$,
Abani Patra$^{(19)}$,
Miguel de Val-Borro$^{(20)}$
}

%
\thanks{{}$^{(1)}$ \hspace{-1ex}Computation Institute, 
University of Chicago \& Argonne National Laboratory, Chicago, IL, USA; d.katz@ieee.org}
%
\thanks{{}$^{(2)}$ NORC at the University of Chicago and Illinois Institute of Technology, Chicago, IL, USA; sctchoi@uchicago.edu}
%
\thanks{{}$^{(3)}$ School of Mechanical, Industrial, and Manufacturing Engineering, 
Oregon State University, Corvallis, OR, USA; kyle.niemeyer@oregonstate.edu}
%
\thanks{{}$^{(4)}$ Research Software Development Group, University College London, UK; j.hetherington@ucl.ac.uk}
%
\thanks{{}$^{(5)}$ \hspace{-1.5ex}Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA; \{knarf,sbrandt\}@cct.lsu.edu}
%
\thanks{{}$^{(6)}$ Lawrence Berkeley National Laboratory, Berkeley, USA; dkgunter@lbl.gov}
%
\thanks{{}$^{(7)}$ RENCI, University of North Carolina at Chapel Hill, Chapel Hill, NC, USA; rayi@renci.org}
%
\thanks{{}$^{(8)}$ University of California, San Diego, CA, USA; mmiller@sdsc.edu}
%
\thanks{{}$^{(9)}$ Center for Research Computing, University of Notre Dame, Notre Dame, IN, USA; sandra.gesing@nd.edu}
%
\thanks{{}$^{(10)}$ New Zealand eScience Infrastructure (NeSI), University of Auckland, Auckland, NZ; nick.jones@nesi.org.nz}
%
\thanks{{}$^{(11)}$ University of Washington, Seattle, WA, USA; nmweber@uw.edu}
%
\thanks{{}$^{(12)}$ Indiana University, Bloomington, IN, USA; smarru@iu.edu}
%
\thanks{{}$^{(13)}$ National Center for Supercomputing Applications, University of Illinois at Urbana-Champaign, Urbana, IL, USA; gdallen@illinois.edu}
%
\thanks{{}$^{(14)}$ College of Computer Engineering \& Computer Science, California State University, Long Beach, CA, USA; birgit.penzenstadler@csulb.edu}
%
\thanks{{}$^{(15)}$ School of Computing and Engineering, University of Huddersfield, Huddersfield, UK; c.venters@hud.ac.uk}
%
\thanks{{}$^{(16)}$ UCAR Unidata, Boulder, CO, USA; edavis@ucar.edu}
%
\thanks{{}$^{(17)}$  University of California, Davis, CA, USA; ljhwang@ucdavis.edu}
%
\thanks{{}$^{(18)}$ Science \& Technology Facilities Council, UK; ilian.todorov@stfc.ac.uk}
%
\thanks{{}$^{(19)}$ Mechanical and Aerospace Engineering, University at Buffalo, Buffalo, NY, USA; abani@buffalo.edu}
%
\thanks{{}$^{(20)}$ Department of Astrophysical Sciences, Princeton University, Princeton, NJ, USA; valborro@princeton.edu}
%

@@

Progress in scientific research is dependent on the quality and accessibility of
software at all levels. Hence it is critical to address challenges related to
development, deployment, maintenance, and overall sustainability of reusable
software as well as education around software practices. These challenges can be
technological, policy based, organizational, and educational; and are of
interest to developers (the software community), users (science disciplines),
software-engineering researchers, and researchers studying the conduct of
science (science of team science, science of organizations, science of science
and innovation policy, and social science communities). The WSSSPE1 workshop
engaged a broad scientific community to identify challenges and best practices
in areas of interest to creating sustainable scientific software. WSSSPE2
invited the community to propose and discuss specific mechanisms to move towards
an imagined future for software development and usage in science and
engineering. But WSSSPE2 did not have a good way to enact those mechanisms, or to
encourage the attendees to follow through on their intentions.
